---
title: "Hypothesis Testing - Mathematical Models"
author: "YOUR NAME"
output: 
  github_document:
    toc: true
    toc_depth: 3
---

# Overview

This tutorial will build your understanding of how to conduct a hypothesis test for a single mean using R. Instead of using the Randomization process, you will utilize a mathematical model - one sample t-test.

This tutorial was built using the contents from [problem number 12 in Chapter 19 titled Inference for a Single Mean Hypothesis in Introduction to Modern Statistics](https://openintro-ims.netlify.app/inference-one-mean.html#chp19-exercises).

***Start by changing YOUR NAME to your name. This can be found at the top of this document next to author.***

```{r packages, echo=FALSE, warning=FALSE}
library(tidyverse)
library(openintro)
library(infer)
library(janitor)
library(knitr)
library(kableExtra)
library(gghighlight)
```

# Goals

***By the end of this tutorial you should be able to...***

1.  Ask a statistical question that would lead you conduct a one sample t test.

2.  Explore a numerical variable by generating summary statistics and a histogram.

3.  Conduct a one sample t test using R.

4.  Make a test decision using the output of your code.

# 1: The Case Study and Research Question:

"In this exercise we work with a random sample of 1,000 cases from the dataset released by the United States Department of Health and Human Services in 2014." While you have explored this data before feel free to run the code below to learn more information about the dataset.

```{r the data}
?ncbirths
glimpse(ncbirths)
```

### ***Research Question: "Does the length of a pregnancy tend to be different than 40 weeks?"***

# 2: Explore the sample data

Before you dive into conducting a hypothesis test, first learn about the sample data.

### 2: Tasks and Questions

a.  In the code chunk below, find the mean and standard deviation of the variable `weeks`.

    ```{r summary stats}

    ```

b.  In the code chunk below, construct a histogram for the `weeks` variable.

    ```{r histogram}

    ```

# 3: Conduct a hypothesis test

### 3: Tasks and Questions

a.  State the null and alternative hypotheses.

    Null:

    Alternative (be sure to read the research question closely):

b.  Edit the code below by doing the following

    -   change `NAME_OF_DATASET`

    -   change `NUMERICAL_VARIABLE`

    -   select one of the following `"two.sided", "less", "greater"`. Your selection depends on your alternative hypothesis

    -   change `HYP_POP_MEAN` to the number that is in your hypotheses.

    ```{r t test}

    t.test(NAME_OF_DATASET$NUMERICAL_VARIABLE,
           alternative = c("two.sided", "less", "greater"),
           mu = HYP_POP_MEAN,
           conf.level = 0.95)

    ```

c.  What is the p-value?

d.  Does the confidence interval contain 40 weeks?

e.  Does this sample dataset contain convincing statistical evidence that the average length of pregnancy is not equal to 40 weeks?
